Stage-Splitting a Modal Language

### 2014-07-24 paper/semantics.tex
added more explanation of partial evaluation system

A function $f$ which accepts inputs at both stages \bbone{} and \bbtwo{} can be
given a type of the form $A\to\fut(B\to C)$.%
\cprotect\footnote{We can rewrite \texttt{fexp} in this form, or simply apply
the following higher-order function which makes the adjustment:
\begin{lstlisting} 
let adjust (f : $int * int -> $int) =
  fn (p : int) => 
    next{
      fn (b : int) => 
        prev{f (next {b}, p)}
    }
\end{lstlisting}}
%
Given its stage \bbone\ argument $a:A$, we can evaluate the partially-applied
function:
$\cdot\vdash f~a \mathop{\redonesym} [\xi,v]$.
The result is an environment $\xi$ and a partial value $v$ of type $\fut(B\to
C)$. Next, we reify this environment into a sequence of \verb|let|-bindings
enclosing $v$, via $\reify\xi{v}{f_a}$. A canonical forms theorem on $v$
ensures that the resulting $f_a$ has type $B\to C$ in the residual language.
Finally, given a stage \bbtwo{} argument $b:B$, we can stage-\bbtwo{} evaluate
the ultimate result of the function, $f_a~b \mathop{\tworedsym} c$.

>>>>

We now consider how to use this formal system to encode inputs to partial evaluation and stage-splitting systems.
Recall that in partial evaluation systems, we have a function $f$ for which some input is labeled {\em static} and 
some labeled {\em dynamic}.  Once the static input is provided, we can partially evaluate the function to produce
a residual that depends on only the dynamic input.

By identifying static with stage \bbone\ and dynamic with stage \bbtwo, 
we can encode this sort of system with a function type of the form $A\to\fut(B\to C)$.
\cprotect\footnote{We can rewrite \texttt{fexp} in this form, or simply apply
the following higher-order function which makes the adjustment:
\begin{lstlisting} 
let adjust (f : $int * int -> $int) =
  fn (p : int) => 
    next{
      fn (b : int) => 
        prev{f (next {b}, p)}
    }
\end{lstlisting}}
%
Here $A$ represents the static input, $B$ represents the dynamic input, and $C$ represents the output.

Once a stage \bbone\ argument $a:A$ is provided, we can evaluate the partially-applied
function:
$\cdot\vdash f~a \mathop{\redonesym} [\xi,v]$.
The result is an environment $\xi$ and a partial value $v$ of type $\fut(B\to
C)$. Next, we reify this environment into a sequence of \verb|let|-bindings
enclosing $v$, via $\reify\xi{v}{f_a}$. A canonical forms theorem on $v$
ensures that the resulting $f_a$ has type $B\to C$ in the residual language.
Finally, given a stage \bbtwo{} argument $b:B$, we can stage-\bbtwo{} evaluate
the ultimate result of the function, $f_a~b \mathop{\tworedsym} c$.
